\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}

% fontawesome
\usepackage{fontawesome5}

% fixed width
\usepackage[scale=0.90,lf]{FiraMono}

% light-grey
\definecolor{light-grey}{gray}{0.83}
\definecolor{dark-grey}{gray}{0.3}
\definecolor{text-grey}{gray}{.08}

\DeclareRobustCommand{\ebseries}{\fontseries{eb}\selectfont}
\DeclareTextFontCommand{\texteb}{\ebseries}

% custom underline
\usepackage{contour}
\usepackage[normalem]{ulem}
\renewcommand{\ULdepth}{1.8pt}
\contourlength{0.8pt}
\newcommand{\myuline}[1]{%
  \uline{\phantom{#1}}%
  \llap{\contour{white}{#1}}%
}

% custom font: helvetica-style
\usepackage{tgheros}
\renewcommand*\familydefault{\sfdefault}
\usepackage[T1]{fontenc}

\pagestyle{fancy}
\fancyhf{}
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{0in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% sans serif sections
\titleformat {\section}{
    \bfseries \vspace{2pt} \raggedright \large
}{}{0em}{}[\color{light-grey} {\titlerule[2pt]} \vspace{-6pt}]

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-1pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-1pt}\item
    \begin{tabular*}{\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & {\color{dark-grey}\small #2}\vspace{1pt}\\
      \textit{#3} & {\color{dark-grey} \small #4}\\
    \end{tabular*}\vspace{-4pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
      #1 & {\color{dark-grey}} \\
    \end{tabular*}\vspace{-4pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{0pt}}

\color{text-grey}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{document}
%----------HEADING----------
\begin{center}
    \textbf{\Huge Gutta Bhargav Prudhvi} \\ \vspace{6pt}

    \small
    \faEnvelope \hspace{2pt} \href{mailto:bhargavgutta910@gmail.com}{bhargavgutta910@gmail.com}
    \hspace{8pt} $|$ \hspace{8pt}
    \faPhone* \hspace{2pt} +91 9502980009
    \hspace{8pt} $|$ \hspace{8pt}
    \faGithub \hspace{2pt} \href{https://github.com/Gutta09}{Gutta09}
    \hspace{8pt} $|$ \hspace{8pt}
    \faLinkedin \hspace{2pt} \href{www.linkedin.com/in/bhargavgutta}{Bhargavgutta}
    \hspace{8pt} $|$ \hspace{8pt}
    \faMapMarker* \hspace{2pt} Vijayawada, India
\end{center}

%-----------SUMMARY-----------
\section{SUMMARY}
\small{Computer Science undergraduate at SRM University AP with hands-on experience in full-stack web development, machine learning. Proficient in building end-to-end applications using the MERN stack, Python-based ML pipelines, and cloud CRM solutions. Seeking opportunities to apply technical skills in software engineering and data-driven problem solving.}
\vspace{-6pt}

%-----------EDUCATION-----------
\section{EDUCATION}
\resumeSubHeadingListStart

\item
\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
\textbf{SRM University AP} & \textbf{\textit{B.Tech. Computer Science and Engineering}} \\
Amaravathi, India & \textit{Aug. 2023 -- May 2027} \\
\end{tabular*}\vspace{-6pt}

\resumeItemListStart
    \resumeItem{\textbf{Cumulative GPA:} 7.54/10}
\resumeItemListEnd

\resumeSubHeadingListEnd

%-----------EXPERIENCE-----------
\section{EXPERIENCE}
\resumeSubHeadingListStart

\resumeSubheading
  {Edubot Technologies}{June 2025 – July 2025}
  {Full Stack Developer Intern (MERN Stack)}{Remote}
  \resumeItemListStart
    \resumeItem{Completed an intensive 8-week program focused on MERN stack development (MongoDB, Express.js, React.js, Node.js).}
    \resumeItem{Developed a full-stack Expense Tracker application with frontend using React + Vite (Tailwind CSS) and backend using Node.js/Express.js with MongoDB Atlas.}
    \resumeItem{Implemented responsive UI, client-side routing, and RESTful APIs for adding, tracking, and deleting expenses.}
  \resumeItemListEnd

\resumeSubHeadingListEnd

%-----------PROJECTS-----------
\section{PROJECTS}
    \resumeSubHeadingListStart

      \resumeProjectHeading
          {\textbf{LearnWeave} $|$ \emph{Next.js, TypeScript , PostgreSQL, OpenAI API,} $|$ \href{https://github.com/Gutta09/LearnWave}{\myuline{GitHub}}}{}
          \resumeItemListStart
            \resumeItem{Built an AI-powered course generation platform using Next.js, TypeScript, and OpenAI GPT-4 API that automatically creates complete courses with lessons and YouTube videos from user topics in 2-3 minutes.}
            \resumeItem{Integrated YouTube Data API and OpenAI to automatically recommend relevant educational videos for each lesson with real-time metadata integration and quality filtering.}
          \resumeItemListEnd

      \resumeProjectHeading
          {\textbf{Expense Tracker} $|$ \emph{React, Vite, Tailwind CSS, Node.js, Express.js, MongoDB} $|$ \href{https://github.com/Gutta09/ExpenseTracker}{\myuline{GitHub}}}{}
          \resumeItemListStart
            \resumeItem{Architected and deployed a secure full-stack MERN application with JWT authentication, protected routes, and role-based access control (RBAC).}
            \resumeItem{Implemented centralized state management using React Context API, enabling real-time dashboard updates, advanced filtering, and CSV data export.}
            \resumeItem{Built and documented RESTful APIs with modular controllers and middleware for expense tracking and user management, ensuring scalability and maintainability.}
          \resumeItemListEnd

      \resumeProjectHeading
          {\textbf{RhythmicTunes} $|$ \emph{React, Tailwind CSS, Shadcn/ui, Vite} $|$ \href{https://github.com/Gutta09/RhythmicTunes}{\myuline{GitHub}}}{}
          \resumeItemListStart
            \resumeItem{Created a music streaming app with full playback controls, shuffle, repeat modes, and playlist management using \textbf{React Context API} for state management.}
            \resumeItem{Designed a responsive UI with \textbf{dark/light theme} support, genre-based browsing, artist collections, and a personal library tracking listening statistics.}
          \resumeItemListEnd

    \resumeSubHeadingListEnd

%-----------SKILLS-----------
\section{SKILLS}
 \begin{itemize}[leftmargin=0in, label={}]
    \small{\item{
     \textbf{Languages}{: Python, JavaScript, HTML/CSS, SQL, Go, }\vspace{2pt} \\
     \textbf{Frameworks}{: React.js, Node.js, Express.js, Tailwind CSS, PHP, Astro, }\vspace{2pt} \\
     \textbf{Libraries}{: scikit-learn, Pandas, NumPy, Matplotlib, Seaborn, Socket.io, PixiJS}\vspace{2pt} \\
     \textbf{Databases}{: MongoDB, PostgreSQL, MySQL}\vspace{2pt} \\
     \textbf{Developer Tools}{: Git, GitHub, Jupyter Notebook, VS Code, PowerBi, Lightning App Builder}\vspace{2pt} \\
     \textbf{Concepts}{: Machine Learning, REST APIs, Data Visualization, CRM Development, Responsive Design}
    }}
 \end{itemize}

%-------------------------------------------
\end{document}
